The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-20 paper/sections/methods.tex
typo
VEM note
dave note

\begin{algorithm}[h]
    \label{alg:sem}
    \SetAlgoLined
    \KwResult{Write here the result }
     initialization\;
     \While{While condition}{
      instructions\;
      \eIf{condition}{
       instructions1\;
       instructions2\;
       }{
       instructions3\;
      }
     }
     \caption{SEM Algorithm}
    \end{algorithm}

@@

The remaining step in defining a single element is to describe how to solve for the polynomial coefficients. For a single element, we have $n$ material points $(\mathbf{X}_1 \dots \mathbf{X}_n)$ and their corresponding deformed positions $(\mathbf{x}^*_1 \dots \mathbf{x}^*_n)$. As these elements are defined on a boundary, these are both known throughout the simulation. Therefore we may form a fitting problem to solve for the polynomial coefficients that minimize the error $\sum_i^n ||\mathbf{x}_i^* - \mathbf{X}_i ||^2$.  We minimize this error in a least squares sense where we first form the system
\begin{equation}
\left[\begin{array}{c}
\mathbf{M}(\mathbf{X_1-\bar{X}}) \quad \mathbf{I} \\
\vdots \\
\mathbf{M}(\mathbf{X_i-\bar{X}}) \quad \mathbf{I} \\
\vdots \\
\mathbf{M}(\mathbf{X_n-\bar{X}}) \quad \mathbf{I} \\
\end{array} \right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right] = 
\left[ \begin{array}{c}
\mathbf{x}_1^* \\
\vdots \\
\mathbf{x}_i^* \\
\vdots \\
\mathbf{x}_n^*
\end{array} \right]
\text{,}
\end{equation}
and then in the more compact form
\begin{equation}
\label{eqn:fitting_one}
\left[
\mathbf{A} \quad \mathbf{S}
\right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right] = \mathbf{b}
\text{,}
\end{equation}
where $\mathbf{A}$ is the block containing the monomial matrices of the system, and $\mathbf{S}$ is the block of identity matrices. Next, to reduce the degrees of freedom of this system we let the deformed center of mass (the constant term coefficients), $t$, be equal to the mean of the deformed positions influenced by this center of mass. In the case of one element we have $t = \frac{1}{n}\sum_i^n x_i^*$. We describe the details on center of mass selection in section \myworries{insert here}. In matrix form we have
\begin{equation}
\label{eqn:t_solution}
t = 
\underbrace{
\left[\begin{array}{ccccccc}
\frac{1}{n} & & \cdots \frac{1}{n} & & \\
& \frac{1}{n} & \cdots & \frac{1}{n} & \\
& & \frac{1}{n} \cdots & & \frac{1}{n} \\
\end{array} \right]}_{T} 
\mathbf{b}
\text{.}
\end{equation} (\myworries{spacing on this looks bad....}). Finally, this leaves us with the system
\begin{equation}
\mathbf{A}\mathbf{c}=(\mathbf{I}-\mathbf{ST})\mathbf{b}
\text{.}
\end{equation}
Like in the original Shape Matching \cite{10.1145/1073204.1073216}, we solve for the coefficients by minimizing the error in a least squares sense, resulting in
\begin{equation}
\label{eqn:c_one_element}
\begin{split}
\mathbf{c} & = (\mathbf{A}^T\mathbf{A})^{-1}\mathbf{A}^T(\mathbf{I-ST})\mathbf{b} \\
           & = \mathbf{L}\mathbf{b}
\end{split}
\text{.}
\end{equation}
This $\mathbf{L}$ matrix thus gives us our file ingredient in the element, coefficients defining the polynomial. We emphasize that $\mathbf{L}$ is constant throughout the simulation, therefore as $\mathbf{b}$ varies in the simulation, $\mathbf{Lb}$ gives us a new set of polynomial coefficients as $\mathbf{b}$ changes.

\subsection{Shape Matching Element Method}
\dave{Multiple Parts}
\dave{each polynomial/NURBS tuple is a shape matching element}
\dave{Shape Matching Element assembles global kinematics using blendeded formultion}
 In a typical simulation we will have multiple shape matching elements where the boundary of each element is defined by a different NURBS surface. Therefore for the entire model each shape has a boundary, a polynomial describing its deformation, as well as an associated center of mass. These centers of mass may not be distinct, meaning that a single center of mass may be shared among multiple surfaces. This sharing of center of masses is typical and in some cases required (\myworries{reference center of mass section that describes how for planar surfaces we need to share COM to get a COM out of plane}). This leads to a new definition of the center of mass where it is the mean of all the boundary points associated with it.

>>>>

\begin{algorithm}[h]
    \label{alg:sem}
    \SetAlgoLined
    \KwResult{Write here the result }
     initialization\;
     \While{While condition}{
      instructions\;
      \eIf{condition}{
       instructions1\;
       instructions2\;
       }{
       instructions3\;
      }
     }
     \caption{Shape Matching Element Algorithm}
    \end{algorithm}

@@

The remaining step in defining a single element is to describe how to solve for the polynomial coefficients. For a single element, we have $n$ material points $(\mathbf{X}_1 \dots \mathbf{X}_n)$ and their corresponding deformed positions $(\mathbf{x}^*_1 \dots \mathbf{x}^*_n)$. As these elements are defined on a boundary, these are both known throughout the simulation. Therefore we may form a fitting problem to solve for the polynomial coefficients that minimize the error $\sum_i^n ||\mathbf{x}_i^* - \mathbf{X}_i ||^2$.  We minimize this error in a least squares sense where we first form the system
\begin{equation}
\left[\begin{array}{c}
\mathbf{M}(\mathbf{X_1-\bar{X}}) \quad \mathbf{I} \\
\vdots \\
\mathbf{M}(\mathbf{X_i-\bar{X}}) \quad \mathbf{I} \\
\vdots \\
\mathbf{M}(\mathbf{X_n-\bar{X}}) \quad \mathbf{I} \\
\end{array} \right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right] = 
\left[ \begin{array}{c}
\mathbf{x}_1^* \\
\vdots \\
\mathbf{x}_i^* \\
\vdots \\
\mathbf{x}_n^*
\end{array} \right]
\text{,}
\end{equation}
and then in the more compact form
\begin{equation}
\label{eqn:fitting_one}
\left[
\mathbf{A} \quad \mathbf{S}
\right]
\left[ \begin{array}{c}
\mathbf{c} \\
\mathbf{t} \\
\end{array} \right] = \mathbf{b}
\text{,}
\end{equation}
where $\mathbf{A}$ is the block containing the monomial matrices of the system, and $\mathbf{S}$ is the block of identity matrices. Next, to reduce the degrees of freedom of this system we let the deformed center of mass (the constant term coefficients), $t$, be equal to the mean of the deformed positions influenced by this center of mass. In the case of one element we have $t = \frac{1}{n}\sum_i^n x_i^*$. We describe the details on center of mass selection in section \myworries{insert here}. In matrix form we have
\dave{need to explain that system can be degenerate fix is to select a constant term}
\begin{equation}
\label{eqn:t_solution}
t = 
\underbrace{
\left[\begin{array}{ccccccc}
\frac{1}{n} & & \cdots \frac{1}{n} & & \\
& \frac{1}{n} & \cdots & \frac{1}{n} & \\
& & \frac{1}{n} \cdots & & \frac{1}{n} \\
\end{array} \right]}_{T} 
\mathbf{b}
\text{.}
\end{equation} (\myworries{spacing on this looks bad....}). Finally, this leaves us with the system
\begin{equation}
\mathbf{A}\mathbf{c}=(\mathbf{I}-\mathbf{ST})\mathbf{b}
\text{.}
\end{equation}
Like in the original Shape Matching \cite{10.1145/1073204.1073216}, we solve for the coefficients by minimizing the error in a least squares sense, resulting in
\dave{no b just use J q, here's a good place to explain sampling the surface to build big J.}
\begin{equation}
\label{eqn:c_one_element}
\begin{split}
\mathbf{c} & = (\mathbf{A}^T\mathbf{A})^{-1}\mathbf{A}^T(\mathbf{I-ST})\mathbf{b} \\
           & = \mathbf{L}\mathbf{b}
\end{split}
\text{.}
\end{equation}
This $\mathbf{L}$ matrix thus gives us our file ingredient in the element, coefficients defining the polynomial. We emphasize that $\mathbf{L}$ is constant throughout the simulation, therefore as $\mathbf{b}$ varies in the simulation, $\mathbf{Lb}$ gives us a new set of polynomial coefficients as $\mathbf{b}$ changes.

\dave{Shape Matching is VEM brief explanation here. Point of departure, one polynmoial isn't going to cut it for a whole object.}
\subsection{Shape Matching Element Method}
\dave{Multiple Parts}
\dave{each polynomial/NURBS tuple is a shape matching element}
\dave{Shape Matching Element assembles global kinematics using blendeded formultion}
 In a typical simulation we will have multiple shape matching elements where the boundary of each element is defined by a different NURBS surface. Therefore for the entire model each shape has a boundary, a polynomial describing its deformation, as well as an associated center of mass. These centers of mass may not be distinct, meaning that a single center of mass may be shared among multiple surfaces. This sharing of center of masses is typical and in some cases required (\myworries{reference center of mass section that describes how for planar surfaces we need to share COM to get a COM out of plane}). This leads to a new definition of the center of mass where it is the mean of all the boundary points associated with it.
